Untitled

### 2023-08-12 draft_v0_1.Rmd
Created new draft version for new flow of document. From Windows.

@@

# libraries
library(kableExtra)
library(knitr)
library(tidyverse)

# colours and theme

@@

```{r data_prep}

@@

@@

# prepare ----------------------------------------------------------
  # make month and year columns

@@

unique(dta$month_creation)
dta$month_creation <- factor(dta$month_creation, levels = 1:12,  labels = mnths)
dta$month_completion <- factor(dta$month_completion, levels = 1:12, labels = mnths)

@@

```{r data_checks}
sum(is.na(dta$notification_number))
# no missing notification nrs

# missingness

x <- nrow(dta)

map_dbl(dta, ~sum(is.na(.x))/x) %>% 
  sort()

dta %>% 
  group_by(is.na(directorate), is.na(department), is.na(branch), 
           is.na(section), is.na(official_suburb)) %>% 
  count()

# dates

@@

We investigated missingness that would make interpretation hard.  Entries for which any of the Directorate, Department, Branch, Section or Official suburb were missing are visualised (Figure A). Entries with missing Directorate were in general also missing for the other categories. Entries for which Directorate was missing, but Official suburb was not(n = 1256), accounted for at most 4% of entries for any suburb and the suburb with the highest percentage of missing entries of this kind, was Kewtown(Figure B).

```{r missing1}
tmp <- dta %>% 
  select(directorate, department, branch, section, official_suburb) %>% 
  mutate(across(everything(), ~as.numeric(is.na(.x)))) %>% 
  as.data.frame()

@@

unique(dta$month_creation)

@@

@@

@@

  tabledta <- dataset %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = "ALL COMBINED") %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = "all_codes_combined") %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb, code) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

@@

  tabledta_below <- dataset_x %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = "ALL COMBINED") %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = "all_codes_combined") %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

@@

  tabledta_above <- dataset_x %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = "ALL COMBINED") %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = "all_codes_combined") %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

@@

@@

# START HERE
plot_time_per_var <- function(dataset = plotdta, column = "code_group", hours_cutoff = 96){

>>>>

Describe brief, outline of document.

@@

# libraries
library(kableExtra)
library(knitr)
library(lubridate)
library(tidyverse)

# colours and theme
  # COCT colours

@@

## Methods

Describe data prep, code generalisable, tech details - missingness, exclusion decisions, choice of vars (e.g. code var).

```{r data_prep, results='hide'}
# output from this code chunk should not print in report

@@

# data checks ----------------------------------------

@@

sum(is.na(dta$notification_number))
# no missing notification nrs

  # numeric cols ---------

summary(dta$latitude)
summary(dta$longitude)

  # date cols -----------

unique(lubridate::as_date(dta$creation_timestamp)) 
# none missing
# exlude 1 date in dec-2019
unique(lubridate::as_date(dta$completion_timestamp))
# some NAs, explore later

# create new variables -----------------------------------------

  # make month and year columns ------

@@

dta$month_creation <- factor(dta$month_creation, levels = 1:12,  labels = mnths)
dta$month_completion <- factor(dta$month_completion, levels = 1:12, labels = mnths)

  # make time-to-complete columns ------
  # note %--% is a lubridate-specific operator

dta <- dta %>% 
   mutate(interv = creation_timestamp %--% completion_timestamp,
          time_hours = as.duration(interv) / dhours(1),
          time_days = as.duration(interv) / ddays(1),
          time_weeks = as.duration(interv) / dweeks(1)) %>% 
  select(-interv)

@@

```{r missing1}

n_cutoff <- 5

tmp <- dta %>% 
  group_by(official_suburb) %>% 
  count(name = "total_suburb") %>% 
  inner_join(dta %>% 
  filter(is.na(directorate) & !is.na(official_suburb)) %>% 
  group_by(official_suburb) %>% 
  count(name = "n_missing")) %>% 
  mutate(percentage_missing = n_missing/total_suburb*100) %>% 
  filter(n_missing >= n_cutoff) %>% 
  arrange(desc(percentage_missing), desc(n_missing)) %>% 
  ungroup()

# max(tmp$percentage_missing)
# tmp$official_suburb[tmp$percentage_missing == max(tmp$percentage_missing)]

tmp <- dta %>% 
  select(directorate, department, branch, section, official_suburb) %>% 
  mutate(across(everything(), ~as.numeric(is.na(.x)))) %>% 
  as.data.frame()
head(tmp)

mis_dir_nonmis_sub <- tmp %>% 
  group_by(directorate, official_suburb) %>% 
  count() %>% 
  filter(directorate == 1 & official_suburb == 0) %>% 
  pull(n)

@@

Missingness of specific data entries can be meaningful, e.g. it can point to operational failures if a specific region has more missing data than another.  Therefore it is important to interrogate patterns of missingness in data. We investigated missingness that would make interpretation hard.  Entries for which any of the Directorate, Department, Branch, Section or Official suburb were missing are visualised (Figure A). Entries with missing Directorate were in general also missing for the other categories. Suburbs for which there were at least `r n_cutoff` entries, and for which Directorate was missing, but Official suburb was not(n = `r mis_dir_nonmis_sub`), accounted for at most `r tmp$percentage_missing` of entries for any suburb and the suburb with the highest percentage of missing entries of this kind, was `r tmp$official_suburb[tmp$percentage_missing == max(tmp$percentage_missing)]`(Figure B).

```{r missing2}

@@

@@

# prepare ----------------------------------------------------------

  # exclusions -------

# exclude creation date 2019, as only 31 Dec is represented

dta <- dta %>% 
  filter(creation_timestamp >= lubridate::as_datetime("2020-01-01 00:00:00 UTC"))

@@

  sub_txt <- "ALL COMBINED"
  code_txt <- "All codes combined"

@@

  tabledta <- dataset %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
                 mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb, code) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

@@

  tabledta_below <- dataset_x %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset_x %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
              mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

@@

  tabledta_above <- dataset_x %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset_x %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
              mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

@@

# look at suburbs with n >= 5
# all codes combined

n_cutoff <- 5
sub_txt <- "ALL COMBINED"
code_txt <- "All codes combined"

time_dta_list$all_times %>% 
  filter(official_suburb == sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  kable(caption = "City-wide, all codes combined") %>%
  kable_styling(full_width = FALSE, position = "left")

time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  arrange(desc(med_time_hrs)) %>% 
  slice(1:5) %>% 
  kable(caption = "Top 5 suburbs with long median completion times, all codes combined") %>%
  kable_styling(full_width = FALSE, position = "left")

time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  arrange(med_time_hrs) %>% 
  slice(1:5) %>% 
  kable(caption = "Top 5 suburbs with short median completion times, all codes combined") %>%
  kable_styling(full_width = FALSE, position = "left")

# split by codes
# codes with > 5 requests, per suburb
# show top 5 per code

n_cutoff <- 5
sub_txt <- "ALL COMBINED"
code_txt <- "All codes combined"

tmp <- time_dta_list$all_times %>% 
  filter(official_suburb == sub_txt &
           code != code_txt &
           n >= n_cutoff) %>% 
  arrange(desc(med_time_hrs))

code_txt <- tmp$code[2]

plotdta <- tmp %>% 
  mutate(set = "City-wide") %>% 
  filter(code == code_txt) %>% 
  bind_rows(time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt &
           n != 1) %>% 
  arrange(desc(med_time_hrs)) %>% 
  slice(1:5) %>% 
    mutate(set = "top_long_times")) %>% 
  bind_rows(time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt,
         n != 1) %>% 
  arrange(med_time_hrs) %>% 
  slice(1:5) %>% 
    mutate(set = "top_short_times")) %>% 
  pivot_longer(cols = c(med_time_hrs, q80_time_hrs),
               names_to = "quantile", values_to = "time_hrs")

x <- plotdta %>% 
  filter(quantile == "med_time_hrs") %>% 
  select(official_suburb, time_hrs) %>% 
  arrange(desc(time_hrs)) %>% 
  pull(official_suburb)

plotdta$official_suburb <- factor(plotdta$official_suburb,
                                  levels = unique(x))

plotdta %>% 
  ggplot(aes(time_hrs, official_suburb, colour = set))+
  geom_point()

# per month

@@

plot_time_per_var <- function(dataset = plotdta, column = "code_group", hours_cutoff = 96){
